Komols Complexity, Coresets, and Sketches in Machine Learning

### 2018-12-30 komlos.tex

In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance. For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
The goal is to produce weights $w$ with at most $k \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{n}w_i f(x_i,q)$ approximates $F(q)$.
Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.

Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.

@@

\el{I believe that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets. Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}

@@

If however, we are interested in a high probability bound of $1-\delta$, we decompose the error to two components
$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
 Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later. Notice that the right summand contains roughly $\log(1/\delta)$ random variables. Since they are all Bernoulli we get that any combination of them is possible with probability $\geq \delta$ hence we must use a deterministic bound for these upper layers. We thus set $k_h=k$ for $h > H'$ and use the bound
$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
Now, for the bottom layers we use Chernoffs bound
$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$

@@

Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
$$
We now make use of the above union bound applied to the bound on $n_h$. Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$. We get that since $n_h \leq 3n/2^h$
$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
$$
In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta_1)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta_1/(H'-h+1)^2$$
and a union bound ensures that with probability at least $1-\delta_1$, for any fixed query $q$ it holds for all $h \leq H'$ that
$$\left| \text{Err}_h(q) \right| \geq \eps_h n$$
and 
$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$

@@

\section{Connections to streaming Counting and Quantiles}

\section{Kernel Density Estimation}

Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $\rho: \R^d \rightarrow \R$ of a point $y$ is defined as 
$$ \rho(y) = \sum_{i=1}^{n} K(x_i,y) $$
Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include

$$ K(x,y) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,y) = \exp(- \|x-y\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|/_2^2/\lambda^2)^{-1}$$

where $\lambda$ is a scaling parameter. What we discuss in what follows applies for any positive definite kernel, an depends on a bound on $K(x,x)$. For simplicity we assume that $K(x,x) \leq 1$ for all datapoints. Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.

Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,y)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
$$ K(x,y) = \ip{\phi(x), \phi(y)} $$
Using this function $\phi$ our objective function becomes
$$\sum_{i=1}^m \sigma_i K(x_i,y) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(y)} \leq $$
$$ \|\phi(y)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| \leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| $$
This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
Given $m$ vectors $z_1,\ldots,z_m$ in an inner product space, compute signs minimizing $\| \sum_i \sigma_i z_i \|$.
We first notice that for i.i.d.\ uniform signs, it holds that
$$\E[\| \sum_i \sigma_i z_i \|^2] = \E[\sum_{i,j} \sigma_i \sigma_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i \sigma_i z_i \| \le 2\sqrt{\sum_i \|z_i\|^2}$.
%
We can also use the method of expectation minimization to achieve this bound deterministically.
Specifically, we will guaranty that $\| \sum_{j=1}^i \sigma_j z_j \|^2 \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
This is trivially true for $i=1$. 
For another value $i$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle z_j, z_i \rangle)$ 
and  assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j z_j\|^2 \le \sum_{j=1}^{i-1} \|z_j\|^2$.

\begin{eqnarray*}
\| \sum_{j=1}^{i}\sigma_j z_j\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j z_j\|^2 + \|z_i\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j z_j, \sigma_i z_i\rangle \\
&\le& \sum_{j=1}^{i-1} \|z_j\|^2 + \|z_i\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle \mbox{\;\;\; by the induction assumption}\\ 
&=& \sum_{j=1}^{i} \|z_j\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle| \le \sum_{j=1}^{i} \|z_j\|^2
\end{eqnarray*}
This completes the proof that $\| \sum_{j=1}^{k}\sigma_j z_j\| \le \sqrt{\sum_{j=1}^{i} \|z_j\|^2}$ for our choice of values for $\sigma$. 
%
Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
This guarantees that 
$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$

Using the framework above this provides a streaming coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that 
$\forall \;q\;\; |\tilde \rho(q) - \rho(q)| \le \eps n$.
This matches the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
\zk{We actually ended up using the Radamacher complexity, at least for the bound. Namely, we used random signs. Perhaps there is a kernel for which it is easy to prove something better? One that comes to mind is apx low rank data. By low rank I mean in the kernel space, meaning the $z_i$'s. To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$. Then, we use theory on the sum of unit vectors of low dimension giving $\sqrt{k}/\eps$ where $k$ is the dimension we got. In the worst case if the kernel matrix is isotropic we will get $k \approx n$ and gain nothing, but this way we can squeeze something from the data that wasn't squeezed before.. We can take this further and look into the details of the proof that we can balance unit vectors to have a norm of $\sqrt{d}$ regardless of the number of vectors. The key in that proof is that by considering continuous $s_i$'s we can have the sum equal to zero while keeping only $d$ points with non $\{-1,1\}$ $s_i$'s. Consider a split of top $k$ and bottom rest directions. If we restrict the $s_i$'s to only have the sum to be zero in the top $k$ we get $k$ non integral $s_i$'s but possibly horrible performance on the bottom $k$. What if only restrict $d-2k$ and not $d-k$ points? Then we get some freedom in choosing the integer $s_i$'s. The bound on the bottom singular values can become smaller than the trivial one.}

\section{Universal Coresets for Analytical Functions}

@@

We start some notation and trivial properties. For a vector $q \in \R^d$ let $q^{\otimes k}$ to represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself in all the dimensions. For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
$\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
\begin{lemma}
$\|X\|_{T_k}$ is a norm
\end{lemma}
\begin{proof}
We prove the claim directly from the definition of a norm.
Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$. It follows that there must be $q$ for which it's value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$. For a scalar $a$, we clearly have by definition that
$$ \|aX\|_{T_k} = |a|\|X\|_{T_k} $$
Lastly, by the max definition we clearly have
$$ \|X+Y\|_{T_k} =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq $$
$$\max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$$
\end{proof}

@@

We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$. The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$. Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.

We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
$$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.

>>>>

In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance. For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
The goal is to produce weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.

Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.

@@

@@

If however, we are interested in a smaller sketch with high probability of success of $1-\delta$, we decompose the error to two components
$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
 Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later. Notice that the right summand contains roughly $\log(1/\delta)$ random variables. Since they are all Bernoulli we get that any combination of them is possible with probability $\geq \delta$ hence we must use a deterministic bound for these upper layers. We thus set $k_h=k$ for $h > H'$ and use the bound
$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
Now, for the bottom layers we use Chernoffs bound
$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$

@@

Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
$$
We now make use of the above union bound applied to the bound on $n_h$. Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$. We get that since $n_h \leq 3n/2^h$
$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
$$
In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta_1)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta_1/(H'-h+1)^2$$
and a union bound ensures that with probability at least $1-\delta_1$, for any fixed query $q$ it holds for all $h \leq H'$ that
$$\left| \text{Err}_h(q) \right| \geq \eps_h n$$
and 
$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$

@@

\section{A Simple Algorithm for Kernel Density Estimation}

From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$. This bound is better when the $d > m$. More importantly though, there is a very simple and deterministic algorithm for computing the signs $\sigma$. 
Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
where $\lambda$ is a scaling parameter. For simplicity, we assume that $K(x,x) \leq 1$ for all data points. Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.

Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
Using this function $\phi$ our objective function becomes
\[
\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| 
\]
This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
This is trivially true for $i=1$. 
For another value assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.

\begin{eqnarray*}
\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
\end{eqnarray*}
This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$. 
%
%Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
%The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
%$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
%This guarantees that 
%$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$

Using the framework above this provides a coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$. This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
%\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
%\zk{We actually ended up using the Radamacher complexity, at least for the bound. Namely, we used random signs. Perhaps there is a kernel for which it is easy to prove something better? One that comes to mind is apx low rank data. By low rank I mean in the kernel space, meaning the $\phi(x_j)$'s. To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$. Then, we use theory on the sum of unit vectors of low dimension giving $\sqrt{k}/\eps$ where $k$ is the dimension we got. In the worst case if the kernel matrix is isotropic we will get $k \approx n$ and gain nothing, but this way we can squeeze something from the data that wasn't squeezed before.. We can take this further and look into the details of the proof that we can balance unit vectors to have a norm of $\sqrt{d}$ regardless of the number of vectors. The key in that proof is that by considering continuous $s_i$'s we can have the sum equal to zero while keeping only $d$ points with non $\{-1,1\}$ $s_i$'s. Consider a split of top $k$ and bottom rest directions. If we restrict the $s_i$'s to only have the sum to be zero in the top $k$ we get $k$ non integral $s_i$'s but possibly horrible performance on the bottom $k$. What if only restrict $d-2k$ and not $d-k$ points? Then we get some freedom in choosing the integer $s_i$'s. The bound on the bottom singular values can become smaller than the trivial one.}

\section{Universal Coresets for Analytic Functions of Dot Products}

@@

We start with some notation and trivial properties. 
For a vector $q \in \R^d$ let $q^{\otimes k}$ represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself $k$ times. For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
$\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
\begin{fact}
$\|X\|_{T_k}$ is a norm
\end{fact}
\begin{proof}
We prove the claim directly from the definition of a norm.
Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$. It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$. For a scalar $a$, we clearly have by definition that
$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
$ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
\max_q \left| \langle X, q^{\otimes k}\rangle \right| + \max_q\left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$
\end{proof}

@@

We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
Consider a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$.

A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$. The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$. Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$. 
%
We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$

Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
